---
title: "Untitled"
author: "DM"
date: "2024-03-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


In our WBS ecommerce platform, we extract key characteristics such as total orders, total revenue, best-selling products, and least-selling products, along with identifying top-selling suppliers. We analyze these results across different time series, including seasonally and quarterly, to uncover patterns and trends. Additionally, we examine total revenue by region and assess transaction methods used by various customers. This comprehensive analysis allows us to generate more valuable insights, enhancing our understanding of market dynamics and customer preferences.


```{r}

install.packages("readxl")
install.packages("dplyr")

library(dplyr)
library(ggplot2)
library(tidyr)
library(lubridate)
library(readxl)
library(scales)

```

```{r}
# Reading required database
customers <- read.csv("customers.csv")
order_details <- read.csv("order_details.csv")
orders <- read.csv("orders.csv")
product_categories <- read.csv("product_categories.csv")
products <- read.csv("products.csv")
promotion <- read.csv("promotion.csv")
suppliers <- read.csv("supplier.csv")
transactions <- read.csv("transactions.csv")

```


```{r}
#Standardise date format
orders$order_date <- as.Date(orders$order_date, format= "%d/%m/%Y")
orders$estimated_delivery_date <- as.Date(orders$estimated_delivery_date, format = "%d/%m/%Y")
```


# Total Revenue per Year


```{r}

# Exclude "cancelled" orders and calculate total revenue per year
yearly_revenue <- orders %>%
  filter(order_status != "cancelled") %>%  
  inner_join(order_details, by = "order_id") %>%
  mutate(year = year(order_date)) %>%
  group_by(year) %>%
  summarize(total_revenue = sum(product_price * order_quantity), .groups = 'drop')
print(yearly_revenue)

# Adjusting the total_revenue to be in thousands for visualization
yearly_revenue$total_revenue <- yearly_revenue$total_revenue / 1000

# Plotting line chart for the yearly revenue with y-axis values in thousands

yearly_revenue_plot <- ggplot(yearly_revenue, aes(x = as.factor(year), y = total_revenue, group = 1)) +
  geom_line(color = "blue") +
  geom_point(color = "red", size = 3) +
  labs(title = "Total Revenue per Year (in Thousands)", x = "Year", y = "Total Revenue (Thousands)") +
  theme_minimal() +
  scale_y_continuous(labels = label_number(suffix = "K"), 
                     limits = c(0, max(yearly_revenue$total_revenue, na.rm = TRUE) + 10), 
                     breaks = seq(0, max(yearly_revenue$total_revenue, na.rm = TRUE) + 10, by = 20))


ggsave(plot = yearly_revenue_plot, filename = "figures/yearly_revenue_plot.pdf", width = 10, height = 6, dpi = 300)


```

A continuously decreasing pattern is observed in total revenues per year between 2020 and 2023. Starting at a peak in 2020 with a total revenue of more than £90,000, there is a noticeable year-over-year decrease through to 2023, where the revenue has its lowest value at around £74,000.


# Total Revenue per Quarter Across All Years

```{r}

# Calculate total revenue per quarter across all years

quarterly_revenue <- orders %>%
  filter(order_status != "cancelled") %>%  # Exclude cancelled orders
  inner_join(order_details, by = "order_id") %>%
  mutate(quarter = paste("Q", quarter(order_date), sep="")) %>%
  group_by(quarter) %>%
  summarize(total_revenue = sum(product_price * order_quantity), .groups = 'drop') %>%
  mutate(quarter = factor(quarter, levels = c("Q1", "Q2", "Q3", "Q4")))
print(quarterly_revenue)


quarterly_revenue_all_years_plot <- ggplot(quarterly_revenue, aes(x = quarter, y = total_revenue, group = 1)) +
  geom_line() +
  geom_point() +
  labs(title = "Total Revenue per Quarter Across All Years", x = "Quarter", y = "Total Revenue") +
  theme_minimal() +
  scale_y_continuous(limits = c(0, NA))  # Start y-axis at 0


ggsave(plot = quarterly_revenue_all_years_plot, filename = "figures/quarterly_revenue_all_years_plot.pdf", width = 10, height = 6, dpi = 300)



```

The figure displaying the total revenue per quarter across all years (2020-2023) shows that the sum of the total revenue in all years varies across the quarters, with the highest total revenue recorded in Q2 and the lowest in Q4. It is observed that Q1 has a relatively high total revenue overall, continued with an increasing trend in Q2. However, after Q2, a consistent year-over-year decline in the sum of total revenue values is seen between Q2 and Q4.



# Total Revenue per Quarter 

```{r}

# Calculate the quarterly revenue for each year
detailed_quarterly_revenue <- orders %>%
  filter(order_status != "cancelled") %>%  # Exclude cancelled orders
  inner_join(order_details, by = "order_id") %>%
  mutate(year_quarter = paste(year(order_date), "Q", quarter(order_date), sep="")) %>%
  group_by(year_quarter) %>%
  summarize(total_revenue = sum(product_price * order_quantity), .groups = 'drop') %>%
  arrange(year_quarter)
print(detailed_quarterly_revenue)


detailed_quarterly_revenue <- detailed_quarterly_revenue %>%
  mutate(year = substr(year_quarter, 1, 4),
         quarter = paste("Q", substr(year_quarter, 6, 7), sep=""))  # Add "Q" prefix to quarter


# Plot the line chart for quarterly revenue for each year
quarterly_revenue_plot <- ggplot(detailed_quarterly_revenue, aes(x = quarter, y = total_revenue, group = year, color = year)) +
  geom_line() +  
  geom_point() +
  labs(title = "Total Revenue by Quarter (2020-2023)", x = "Quarter", y = "Total Revenue") +
  scale_color_manual(values = c("2020" = "blue", "2021" = "red", "2022" = "green", "2023" = "purple")) +  
  theme_minimal()

ggsave(plot = quarterly_revenue_plot, filename = "figures/quarterly_revenue_plot.pdf", width = 10, height = 6, dpi = 300)


```

Analyzing the total revenue trends from 2020 to 2023, a recurrent increase is observed from Q1 to Q2 each year except in 2023, where a drop is observed from around £25,000 to £20,000. The transition from Q2 to Q3 in 2022 is marked by a significant rise from around £18,000 to £25,000, contrasted by 2023's sharp decline from around £20,000 to £10,000. While Q3 generally records the peak revenue, especially in 2022; Q4 often sees a decrease, except for 2023, where a rebound to around £18,000 defies the usual downward trend.


# Total Revenue By City

```{r}

# Filter out cancelled orders
non_cancelled_orders <- orders %>%
  filter(order_status != "cancelled")

# Join non_cancelled_orders with order_details
total_revenue_by_city <- non_cancelled_orders %>%
  inner_join(order_details, by = "order_id") %>%
  group_by(city) %>%
  summarize(total_revenue = sum(product_price * order_quantity), .groups = 'drop')
print(total_revenue_by_city)

# Plot the bar chart for total revenue by city
revenue_by_city_plot <- ggplot(total_revenue_by_city, aes(x = reorder(city, total_revenue), y = total_revenue, fill = city)) +
  geom_col() +
  labs(title = "Total Revenue by City between 2020-2023", x = "City", y = "Total Revenue") +
  theme_minimal() +
  coord_flip() +
  guides(fill = "none")  # Removes the legend

ggsave(plot = revenue_by_city_plot, filename = "figures/revenue_by_city_plot.pdf", width = 10, height = 6, dpi = 300)

```

Analyzing the total revenue across different cities, Belfast emerges on the top with approximately £41,000, while the other cities exhibit varied results. Cardiff and Birmingham also showcase strong revenues, with around £39,000 and £36,000, respectively. London and Manchester, notable for their economic significance, are at the lower end among the first 10 cities listed, each with around £24,000 to £25,000. Geographically, this indicates a diverse economic landscape, with the highest revenues not necessarily in the traditionally dominant economic centers of the UK.


#Transaction Methods Based on Customers

```{r}

# Excluding the cancelled orders and calculate the numbers for each transaction method used
non_cancelled_orders <- orders %>%
  filter(order_status != "cancelled")
transactions_summary <- non_cancelled_orders %>%
  inner_join(transactions, by = "order_id") %>%
  group_by(transaction_method) %>%
  summarize(number_of_transactions = n(), .groups = 'drop')

# Find the maximum number of transactions
max_transactions <- max(transactions_summary$number_of_transactions)

# Bar chart for usage of transaction methods
transaction_methods_plot <- ggplot(transactions_summary, aes(x = reorder(transaction_method, number_of_transactions), y = number_of_transactions, fill = transaction_method)) +
  geom_col(width = 0.5) +  
  geom_text(aes(label = number_of_transactions), vjust = -0.3, color = "black", size = 3.5) + 
  labs(title = "Transaction Methods Based on Customers", 
       x = "Transaction Method",
       y = "Number of Transactions",
       fill = "Transaction Method") +
  theme_minimal() +
  scale_y_continuous(breaks = seq(0, max_transactions, by = 150))

ggsave(plot = transaction_methods_plot, filename = "figures/transaction_methods_plot.pdf", width = 10, height = 6, dpi = 300)

```

Transaction data from our e-commerce platform reveals a balanced preference for payment methods. PayPal leads marginally with 210 transactions, followed by bank transfers at 208 and credit cards at 190.



#Total Orders per Year


```{r}

# Exclude "cancelled" orders and calculate the toal orders per year
yearly_orders_quantity <- orders %>%
  filter(order_status != "cancelled") %>%  
  inner_join(order_details, by = "order_id") %>%
  mutate(year = year(order_date)) %>%
  group_by(year) %>%
  summarize(total_quantity = sum(order_quantity), .groups = 'drop')  # Summarize by total quantity
print(yearly_orders_quantity)

# Plotting the total orders per year
yearly_orders_plot <- ggplot(yearly_orders_quantity, aes(x = as.factor(year), y = total_quantity, group = 1)) +
  geom_line(color = "blue") +
  geom_point(color = "red", size = 3) +
  labs(title = "Total Orders per Year", x = "Year", y = "Total Quantity Sold") +
  theme_minimal() +
  scale_y_continuous(limits = c(0, NA), breaks = seq(0, 500, by = 100))

ggsave(plot = yearly_orders_plot, filename = "figures/yearly_orders_plot.pdf", width = 10, height = 6, dpi = 300)

```

Total order numbers has the lowest value in 2021 and peak value in 2022, starting  with a slight decline from 627 orders in 2020 to 567 in 2021, followed by a significant increase to 643 orders in 2022, and a subsequent decrease to 631 orders in 2023.




#Total Orders per Season


```{r}
# Calculate total orders per season for 4 different years, excluding cancelled orders

detailed_seasonal_orders_quantity <- orders %>%
  filter(order_status != "cancelled") %>%
  inner_join(order_details, by = "order_id") %>%
  mutate(year = year(order_date),
         month = month(order_date),
         season = case_when(
           month %in% c(12, 1, 2) ~ "Winter",
           month %in% c(3, 4, 5) ~ "Spring",
           month %in% c(6, 7, 8) ~ "Summer",
           month %in% c(9, 10, 11) ~ "Fall"
         )) %>%
  mutate(season = factor(season, levels = c("Fall", "Winter", "Spring", "Summer"))) %>%
  group_by(year, season) %>%
  summarize(total_quantity = sum(order_quantity), .groups = 'drop')  # Summarize by total quantity
print(detailed_seasonal_orders_quantity)

# Plotting the  seasonal orders for each year
seasonal_orders_plot <- ggplot(detailed_seasonal_orders_quantity, aes(x = season, y = total_quantity, color = as.factor(year), group = year)) +
  geom_line() + 
  geom_point() +
  scale_color_manual(values = c("2020" = "blue", "2021" = "red", "2022" = "green", "2023" = "purple"),
                     name = "Year") + 
  labs(title = "Total Orders by Season (2020-2023)", 
       x = "Season", 
       y = "Total Quantity Sold",
       color = "Year") +
  theme_minimal()

ggsave(plot = seasonal_orders_plot, filename = "figures/seasonal_orders_plot.pdf", width = 10, height = 6, dpi = 300)

```
The seasonal trend for total orders from 2020 to 2023 shows considerable variability, with no consistent pattern emerging across the years. The spring of 2020 marked the highest number of orders at 681, suggesting a seasonal peak at that time. Notably, orders in the fall have shown growth, particularly from 2021 to 2022 where they rose from 119 to 188. The winter of 2022 also experienced a significant rise to 160 orders, exceeding the counts of both preceding years. Conversely, the summer of 2023 saw a decline to 144 orders, substantially lower than the previous year's 158, indicating a reduction in demand or the impact of other variables.



# Top 5 Best-Selling Products

```{r}

# Exclude "cancelled" orders
non_cancelled_orders <- orders %>%
  filter(order_status != "cancelled")

# Calculate total quantity sold for each product and find the top 5 best-selling products
top_selling_products <- non_cancelled_orders %>%
  inner_join(order_details, by = "order_id") %>%
  group_by(product_id) %>%
  summarise(total_quantity_sold = sum(order_quantity, na.rm = TRUE)) %>%
  ungroup() %>%
  arrange(desc(total_quantity_sold)) %>%
  slice_max(order_by = total_quantity_sold, n = 5) %>%
  distinct(product_id, .keep_all = TRUE)

# Join with the products data frame to get the product names
top_selling_products_with_names <- top_selling_products %>%
  left_join(products, by = "product_id") %>%
  select(product_name, total_quantity_sold) %>%
  arrange(desc(total_quantity_sold)) %>%
  slice_head(n = 10)
print(top_selling_products_with_names)




```


```{r}

# Generate the bar chart r for the top 5 best-selling products

best_selling_products_plot <- ggplot(top_selling_products_with_names, aes(x = reorder(product_name, total_quantity_sold), y = total_quantity_sold, fill = product_name)) +
  geom_bar(stat = "identity") +
  coord_flip() + # Flip the axes to make it a horizontal bar chart
  geom_text(aes(label = scales::comma(total_quantity_sold)), position = position_dodge(width = 0.9), hjust = -0.2, size = 3) +
  labs(title = "Top 5 Best-Selling Products", x = "Product Name", y = "Total Quantity Sold") +
  scale_y_continuous(labels = scales::comma) + # Format the Y axis labels with commas
  scale_fill_brewer(palette = "Set3") +
  theme_minimal() +
  theme(axis.text.y = element_text(angle = 0), legend.position = "none")

ggsave(plot = best_selling_products_plot, filename = "figures/best_selling_products_plot.pdf", width = 10, height = 6, dpi = 300)

```
The 5 top-selling products from e-commerce store are ranked as follows:"Whole Grain Bread 4zv" at 38 units, "Yoga Mat WZQ" at 36, "The Great Adventure EIO" at 35, "Yoga Mat 6ne" at 33, and both "Organic Honey H4w" and "Eau de Toilette MZw" at 32 units each.



#Top 5 Selling Products per Season Across All Years

```{r}

# Ensure order_date is Date type and calculate season
orders <- orders %>%
  mutate(
    order_date = as.Date(order_date, format = "%Y-%m-%d"), # Convert order_date to Date type
    season = case_when(
      month(order_date) %in% c(12, 1, 2) ~ "Winter",
      month(order_date) %in% c(3, 4, 5) ~ "Spring",
      month(order_date) %in% c(6, 7, 8) ~ "Summer",
      month(order_date) %in% c(9, 10, 11) ~ "Fall"
    )
  )

# Filter out cancelled orders from the orders dataframe
non_cancelled_orders <- orders %>%
  filter(order_status != "cancelled")

# Join non_cancelled_orders with order_details and then with products to get product names
sales_data <- non_cancelled_orders %>%
  inner_join(order_details, by = "order_id") %>%
  inner_join(products, by = "product_id")

# Group by season and product_name to summarize total quantity sold across all years
seasonal_sales <- sales_data %>%
  group_by(season, product_name) %>%
  summarise(total_quantity_sold = sum(order_quantity, na.rm = TRUE), .groups = "drop")

# For each season, find the top 10 products with the highest total quantity sold
top_5_seasonal_sales <- seasonal_sales %>%
  arrange(season, desc(total_quantity_sold)) %>%
  group_by(season) %>%
  slice_max(order_by = total_quantity_sold, n = 5, with_ties = FALSE) %>%
  ungroup()

# Print the top 10 best-selling products for each season across all years
print(top_5_seasonal_sales)



```

Throughout 2020 to 2023, Whole Grain Bread 4zv" is a consistent favorite, leading in fall with 16 units and remaining strong in summer with 13. "Organic Honey" is a fall staple, with two varieties selling 13 and 11 units respectively, while "Camping Tent gTa" tops spring sales at 17 units, aligning with outdoor activity in warmer weather. Tech products peak in summer and winter, with "Smartphone X12 Jmx" selling 15 units in summer and "Eau de Toilette MZw" becoming the winter favorite at 14 units. These patterns suggest a blend of steady demand for consumables and seasonal shifts towards outdoor gear and personal electronics.



#Least Selling Product

```{r}

# Filter out cancelled orders
non_cancelled_orders <- orders %>%
  filter(order_status != "cancelled")

# Calculate total quantity sold for each product
product_sales <- non_cancelled_orders %>%
  inner_join(order_details, by = "order_id") %>%
  group_by(product_id) %>%
  summarise(total_quantity_sold = sum(order_quantity, na.rm = TRUE)) %>%
  ungroup()

# join with the 'products' data frame to get the product names
product_sales_with_names <- product_sales %>%
  left_join(products, by = "product_id") %>%
  select(product_name, product_id, total_quantity_sold)

# Arrange the data by total quantity sold to find the least selling products
least_selling_products <- product_sales_with_names %>%
  arrange(total_quantity_sold) %>%
  slice_head(n = 3)

# Print the least selling products excluding cancelled orders
print(least_selling_products)



```

In our e-commerce store, the products 'The Great Adventure Lfr,' 'Smartphone X12 qbk,' 'The Great Adventure zve' 'Premium Blender OaQ,' and 'Camping Tent UeT' have the lowest sales, with only one unit sold for each.


# Best Selling Product Category


```{r}

# Filter out cancelled orders 
non_cancelled_orders <- orders %>%
  filter(order_status != "cancelled")

# Join non_cancelled_orders with order_details, then join with products
sales_data <- non_cancelled_orders %>%
  inner_join(order_details, by = "order_id") %>%
  inner_join(products, by = "product_id")

# Join sales data with product categories to get category names
sales_data_with_categories <- sales_data %>%
  inner_join(product_categories, by = "category_id")

# Aggregate total sales per category, considering the quantity sold and the product price
category_sales_totals <- sales_data_with_categories %>%
  group_by(category_name) %>%
  summarise(total_sales = sum(order_quantity, na.rm = TRUE)) %>%
  ungroup()

# Sort to find the best-selling categories
best_selling_category <- category_sales_totals %>%
  arrange(desc(total_sales)) %>%
  slice_head(n = 5)

# Print the top 5 best-selling product categories
print(best_selling_category)


# Plot the bar chart
best_selling_categories_plot <- ggplot(best_selling_category, aes(x = total_sales, y = reorder(category_name, total_sales), fill = category_name)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = total_sales, y = reorder(category_name, total_sales)), 
            position = position_dodge(width = 0.9), 
            hjust = -0.1, 
            size = 3.5, 
            color = "black") +
  labs(title = "Best Selling Product Category",
       x = "Total Sales", 
       y = "Product Category") +
  theme_minimal() +
  theme(legend.position = "none")

ggsave(plot = best_selling_categories_plot, filename = "figures/best_selling_categories_plot.pdf", width = 10, height = 6, dpi = 300)


```
The cumulative sales data shows that "Groceries" is the leading category with a total of 420 units sold, closely followed by "Fashion" at 369 units. "Sports & Outdoors" is also strong with 355 units sold. "Beauty & Personal Care" and "Home & Kitchen" have lower sales in comparison, at 296 and 284 units respectively.


# Best Selling Product Category per Season


```{r}

# Ensure order_date is Date type and define seasons
orders <- orders %>%
  mutate(
    order_date = as.Date(order_date, format = "%Y-%m-%d"),
    season = case_when(
      month(order_date) %in% c(12, 1, 2) ~ "Winter",
      month(order_date) %in% c(3, 4, 5) ~ "Spring",
      month(order_date) %in% c(6, 7, 8) ~ "Summer",
      month(order_date) %in% c(9, 10, 11) ~ "Fall"
    )
  )

# Exclude "cancelled" orders
non_cancelled_orders <- orders %>%
  filter(order_status != "cancelled")

#Join the order details with non_cancelled_orders and products to get category_id for each product sold
sales_data <- order_details %>%
  inner_join(non_cancelled_orders, by = "order_id") %>%
  inner_join(products, by = "product_id")

# Join the sales data with product categories to get category names
category_sales_data <- sales_data %>%
  inner_join(product_categories, by = "category_id")

# Aggregate the total sales per category per season
category_season_sales_totals <- category_sales_data %>%
  group_by(season, category_name) %>%
  summarise(total_sales = sum(order_quantity, na.rm = TRUE)) %>%
  ungroup()

# Find the top 5 categories with the highest total sales for each season
best_selling_categories_per_season <- category_season_sales_totals %>%
  arrange(desc(total_sales)) %>%
  group_by(season) %>%
  slice_max(order_by = total_sales, n = 5) %>%
  ungroup()

# Arrange the result in order
best_selling_categories_per_season <- best_selling_categories_per_season %>%
  arrange(season, desc(total_sales))
print(best_selling_categories_per_season)



```

In the fall, Groceries lead the best-selling product category with 120 units, followed by Fashion at 103, and Sports & Outdoors at 83 units. Beauty & Personal Care and Home & Kitchen also perform well with 80 and 74 units respectively. In the spring, Groceries again top the list with 113 units, while Sports & Outdoors rise to a close second with 103 units, overtaking Fashion which is at 99 units. Toys & Games and Books show strong sales in spring, at 91 and 90 units, indicating a surge in leisure and educational activities. This pattern suggests that essentials like groceries have a steady demand, while other categories like Sports & Outdoors and Books gain seasonal traction.

#Total Sales per Supplier per Year

```{r}

# Ensure order_date is Date type
orders <- orders %>%
  mutate(
    order_date = as.Date(order_date, format = "%Y-%m-%d"),
    year = year(order_date)
  )

# Exclude "cancelled" orders
non_cancelled_orders <- orders %>%
  filter(order_status != "cancelled")


# Calculate the total sales per supplier per year
supplier_sales <- order_details %>%
  inner_join(non_cancelled_orders, by = "order_id") %>%
  inner_join(products, by = "product_id") %>%
  group_by(year, supplier_id) %>%
  summarise(total_sales = sum(order_quantity, na.rm = TRUE)) %>%
  ungroup()


supplier_sales <- supplier_sales %>%
  inner_join(suppliers, by = "supplier_id") %>%
  select(year, supplier_name, total_sales) %>%
  arrange(year, desc(total_sales))

# For each year, get the best-selling suppliers
best_selling_suppliers_per_year <- supplier_sales %>%
  group_by(year) %>%
  slice_max(order_by = total_sales, n = 1) %>%
  ungroup()

print(best_selling_suppliers_per_year)

```

The top supplier sales per year show 'Martin-Barnett' leading in 2020 with 15 sales, a dip to 11 sales with 'Archer LLC' in 2021, a Harvey-Hines at 17 sales among suppliers in 2022, and a return to 15 sales with 'Perkins Mathews and Ray' in 2023.


#Total Sales per Supplier per Season

```{r}


# Ensure order_date is Date type and define seasons
orders <- orders %>%
  mutate(
    order_date = as.Date(order_date, format = "%d/%m/%Y"), # Adjust format as necessary
    season = case_when(
      month(order_date) %in% c(12, 1, 2) ~ "Winter",
      month(order_date) %in% c(3, 4, 5) ~ "Spring",
      month(order_date) %in% c(6, 7, 8) ~ "Summer",
      month(order_date) %in% c(9, 10, 11) ~ "Fall"
    )
  )

# Exclude "cancelled" orders
non_cancelled_orders <- orders %>%
  filter(order_status != "cancelled")


# Calculate the total sales per supplier per season
seasonal_supplier_sales <- order_details %>%
  inner_join(non_cancelled_orders, by = "order_id") %>%
  inner_join(products, by = "product_id") %>%
  group_by(season, supplier_id) %>%
  summarise(total_sales = sum(product_quantity, na.rm = TRUE), .groups = "drop") %>%
  ungroup()

# Join with the suppliers dataframe to get the supplier names
seasonal_supplier_sales <- seasonal_supplier_sales %>%
  inner_join(suppliers, by = "supplier_id") %>%
  select(season, supplier_name, total_sales) %>%
  arrange(season, desc(total_sales))

# For each season, find the best-selling suppliers
best_selling_suppliers_per_season <- seasonal_supplier_sales %>%
  group_by(season) %>%
  slice_max(order_by = total_sales, n = 1) %>%
  ungroup()

print(best_selling_suppliers_per_season)


```

Across the seasons from 2020 to 2023, 'Dyer Pena and Johnson' was the top supplier in both fall with 390 sales, while 'Casey Group' led in the spring with the highest sales at 388, and 'Moon Gillespie and Vargas' was the top in summer with 402 sales, lastly in the winter 'Glover-Russell'lead with the total sales of 279


#Conclusion and Future Improvements

Our analysis of the WBS e-commerce platform from 2020 to 2023 reveals a downward trend in annual revenue, with seasonal and quarterly variations. Various analysis conducted on the data on subjects such as on transaction methods and leading cities in revenue generation, revealed a slight preference for PayPal and identified Belfast as an unexpected frontrunner in sales, surpassing major economic centers like London and Manchester. The fluctuating demand across seasons and the identification of best and least-selling products offer strategic insights for the company.
To counter the trend of declining revenue and capitalize on market dynamics, a multifaceted approach is needed. This includes product discounts, product diversification, and the enhancement of payment options to spur future growth. Additionally, a comprehensive market analysis should be undertaken to reassess product offerings and explore new market segments. The analysis of quarterly revenue and seasonal sales underscores the necessity of adaptive strategies to navigate the cyclical nature of sales effectively, optimizing revenue generation year-round. Moreover, exploring the unique revenue trends and market dynamics of each city is essential for creating tailored strategies that meet regional demands and consumer preferences. 

Overall, our detailed report highlights the critical improvement on market segmentation and data-informed decision-making to address e-commerce challenges effectively and foster long-term expansion in the market.




Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
